### 2024-07-24 modern-portfolio-theory.qmd
Built site for gh-pages

@@

In terms of diversification, it can be helpful to diversify in multiple ways.
First, it can be helpful not to rely on just one or two "stud" players.
If they are on bye or have a down week, your team is more likely to suffer.
Also, there are risks in picking multiple offensive players from the same team.
For instance, if you have the Quarterback and Wide Receiver from the same team, and the team has a poor offensive outing, that will have a greater impact.
Having multiple players on a juggernaut offense can be a boon, but it can be challenging to predict which offense will lead the league.

>>>>

Selecting players for your fantasy team is like picking stocks.
Your goal is to pick assets (i.e., players/stocks) that will perform best and that others undervalue.
But what is the best way to do that?
You could do lots of research to pick players/stocks with strong fundamentals that you think will do particularly well next year.
By picking these players/stocks, you are predicting that they will *outperform* their expectations.
However, all of your information is likely already reflected in the current valuation of the player/stock, so your prediction is basically a gamble.
This is evidenced by the fact that people do not reliably beat the crowd/market.

Even so-called experts do not beat the market reliably.
There is little consistency in the performance of mutual fund managers over time.
The following charts are from Leonard Mlodinow's book, "The Drunkard's Walk: How Randomness Rules Our Lives".
The chart on the left depicts the performance of the top mutual funds from 1991 to 1995.
The chart on the right depicts the performance of the same funds in the same order over the subsequent 5 years (1996 to 2000):

The best funds from 1991–1995 weren not necessarily the best funds from 1996–2000.
This suggests that mutual fund managers differ in great part because of luck or chance rather than reliable skill.
That is likely why [a cat beat professional investors in a stock market challenge](http://www.npr.org/blogs/money/2013/01/14/169326326/housecat-beats-investors-in-stock-market-challenge) (archived at <https://perma.cc/R3XU-K6J8>).
Although our sample size is much smaller with fantasy football projections, there also appears to be little consistency in fantasy football sites' rank in accuracy over time [INSERT], suggesting that the projection sources are not reliably better than each other (or the crowd) over time.

The market reflects all of the knowledge of the crowd.
One common misconception is that if you go with the market, you will receive "average" returns (by "average", I mean that you will be in the 50th percentile among investors).
This is not true—it has been shown that most mutual funds (about 80%) underperform the average returns of the stock market.
So, by going with the market average, you will likely perform better than the "average" fund/investor.
Consistent with this, crowd-averaged fantasy football projections tend to be more accurate than any individual's projection: INSERT
This evidence is consistent with the notion of the wisdom of the crowd.

@@

Another important lesson from investing is diversification.
If you have too much money in one asset and that asset tanks, you will lose your money.
In other words, you do not want to put all of your eggs in one basket.
By owning different asset classes (e.g., domestic and international stocks and bonds), you can limit your downside risk without sacrificing much in terms of expected return.

This lesson can also apply to fantasy football.
In terms of diversification, it can be helpful to diversify in multiple ways.
First, it can be helpful not to rely on just one or two "stud" players.
If they are on bye or have a down week, your team is more likely to suffer.
Also, there are risks in picking multiple offensive players from the same team.
If you draft your starting Quarterback and Wide Receiver from the same team (e.g., the Cowboys), you are exposing your fantasy team to considerable risk.
For instance, if you have the Quarterback and Wide Receiver from the same team, and the team has a poor offensive outing, that will have a greater impact.
You can limit your downside risk by diversifying—drafting players from different teams.
That way if the Cowboys' offense does poorly in a given week, your fantasy team will not be as affected.
Having multiple players on a juggernaut offense can be a boon, but it can be challenging to predict which offense will lead the league.

However, sometimes having two players on the same team might be beneficial because some positions may be uncorrelated or even negatively correlated, which can also reduce risk.
For instance, the performance of the Tight End and Running Back on the same team tends to be slightly negatively correlated, so it might not be a bad idea to start the Tight End and Running Back from the same team.
For a correlation matrix of all positions on the team, see INSERT
